---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
# Setup for targets:

library(targets)
tar_config_set(store = "../_targets")
tar_load(c(ipums_occupations, americanstories_mentions, occupation_language_bridge))
# You can interact with tar objects as usual, e.g.:
# print(ipums_occupations)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.2, @vanlissaWORCSWorkflowOpen2021] to ensure reproducibility and transparency.


This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data.-->
`r notify_synthetic()`

## Analysis Plan

This analysis links two views of occupational devaluation between 1850 and 1880:
IPUMS census microdata, which gives weighted occupational composition, and
American Stories keyword-in-context rows, which give newspaper language around
selected occupations.

## IPUMS Occupational Composition

```{r ipums-occupations}
head(ipums_occupations, 20)
```

## American Stories Mentions

```{r americanstories-mentions}
head(americanstories_mentions, 20)
```

## Matched Occupation-Language View

```{r bridge}
head(occupation_language_bridge, 20)
```
